|

### 2022-06-23 docs/rmd/paper.Rmd
autogit

All GP experiments will be implemented by using the python programming language in conjunction with DEAP, a framework for distributed evolutionary algorithms that implements various tools and algorithms for genetic programming [@DEAP_JMLR2012]. A github repository that contains the full source code, tables, plots and other materials represented in this thesis can be accessed at [https://github.com/roman91DE/intelligent_information_systems_research_project](#https://github.com/roman91DE/intelligent_information_systems_research_project).

@@

<!-- ![Mean Size](./plots/size_subplotted.png)--->

@@

To gain further insight into the differences in generalization behavior and to adress the research question with a higher level of certainty, the experiment I conducted should be repeated for different GP configurations. Some exemplary parameters that could drastically influence the results of this experiment include the population size, the total number of generations, the inclusion of elitism or the computation of $\epsilon$ in lexicase selection. Other factors whose influence on generalization behavior could be important include different methods to compute an individuals fitness (e.g. mean absolute error or root mean squared error), testing different variations of the genetic operators for mutation and crossover and experimenting with different variations of the training:testing split size.

>>>>

All GP experiments will be implemented by using the python programming language in conjunction with DEAP, a framework for distributed evolutionary algorithms that implements various tools and algorithms for genetic programming [@DEAP_JMLR2012]. A repository that contains the full source code, tables, plots and other materials represented in this thesis is available at github.com^[https://github.com/roman91DE/intelligent_information_systems_research_project].

@@

<!-- ![Mean Size](./plots/size_sub plotted.png)--->

@@

To gain further insight into the differences in generalization behavior and to address the research question with a higher level of certainty, the experiment I conducted should be repeated for different GP configurations. Some exemplary parameters that could drastically influence the results of this experiment include the population size, the total number of generations, the inclusion of elitism or the computation of $\epsilon$ in lexicase selection. Other factors whose influence on generalization behavior could be important include different methods to compute an individuals fitness (e.g. mean absolute error or root mean squared error), testing different variations of the genetic operators for mutation and crossover and experimenting with different variations of the training:testing split size.

### 2022-06-23 docs/rmd/paper.tex
autogit

All GP experiments will be implemented by using the python programming
language in conjunction with DEAP, a framework for distributed
evolutionary algorithms that implements various tools and algorithms for
genetic programming (Fortin \emph{et al.}, 2012). A github repository
that contains the full source code, tables, plots and other materials
represented in this thesis can be accessed at
\protect\hyperlink{https:ux2fux2fgithub.comux2froman91DEux2fintelligent_information_systems_research_project}{https://github.com/roman91DE/intelligent\_information\_systems\_research\_project}.

@@

To gain further insight into the differences in generalization behavior
and to adress the research question with a higher level of certainty,
the experiment I conducted should be repeated for different GP
configurations. Some exemplary parameters that could drastically
influence the results of this experiment include the population size,
the total number of generations, the inclusion of elitism or the
computation of \(\epsilon\) in lexicase selection. Other factors whose
influence on generalization behavior could be important include
different methods to compute an individuals fitness (e.g.~mean absolute
error or root mean squared error), testing different variations of the
genetic operators for mutation and crossover and experimenting with
different variations of the training:testing split size.

>>>>

All GP experiments will be implemented by using the python programming
language in conjunction with DEAP, a framework for distributed
evolutionary algorithms that implements various tools and algorithms for
genetic programming (Fortin \emph{et al.}, 2012). A repository that
contains the full source code, tables, plots and other materials
represented in this thesis is available at github.com\footnote{\url{https://github.com/roman91DE/intelligent_information_systems_research_project}}.

@@

To gain further insight into the differences in generalization behavior
and to address the research question with a higher level of certainty,
the experiment I conducted should be repeated for different GP
configurations. Some exemplary parameters that could drastically
influence the results of this experiment include the population size,
the total number of generations, the inclusion of elitism or the
computation of \(\epsilon\) in lexicase selection. Other factors whose
influence on generalization behavior could be important include
different methods to compute an individuals fitness (e.g.~mean absolute
error or root mean squared error), testing different variations of the
genetic operators for mutation and crossover and experimenting with
different variations of the training:testing split size.
